---
title: "Workshop setup"
author: "Kevin Rue-Albrecht, Charlotte Soneson, Federico Marini, and Aaron Lun"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  rmarkdown::html_document:
    highlight: pygments
    toc: true
    toc_float: true
    toc_depth: 3
    fig_width: 5
    number_sections: false
bibliography: "`r file.path(system.file(package='iSEEWorkshop2020', 'vignettes/bib'), 'iSEE-lab.bib')`"
vignette: >
  %\VignetteIndexEntry{Workshop setup}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  cache = FALSE,
  collapse = TRUE,
  comment = "#>",
  crop = NA
)
suppressPackageStartupMessages({
    require(BiocStyle)
})
htmltools::tagList(rmarkdown::html_dependency_font_awesome())
```

```{r, eval=!exists("SCREENSHOT"), include=FALSE}
SCREENSHOT <- function(x, ...) knitr::include_graphics(x)
```

<!-- Fix until BiocStyle is updated with this style. -->
<style>
td > img {
  padding: 0px;
  max-width: 100%;
  display: inline;
}
</style>

# Docker

In the Docker settings menu:

- Open 'Preferences...'
- Navigate to 'Resources'
- Use the slider to set 'Memory' to '4.00 GB'
- Click 'Apply & Restart'

# Workshop

- Run `docker pull iseedevelopers/iseeworkshop2020`
- Run `docker run -e PASSWORD=isee -p 8787:8787 -d --rm iseedevelopers/iseeworkshop2020`.
  Use `-v $(pwd):/home/rstudio` argument to map your local directory to the container. 
- Log in to RStudio at [http://localhost:8787](http://localhost:8787) using username `rstudio` and password `isee`.
  Note that on Windows you need to provide your localhost IP address like `http://191.163.92.108:8787/` - find it using `docker-machine ip default` in Docker's terminal.
- Run `browseVignettes(package = "iSEEWorkshop2020")`.
  Click on one of the links, "HTML", "source", "R code".
  - In case of `The requested page was not found` error, add `help/` to the URL right after the hostname, e.g., <http://localhost:8787/help/library/iSEEWorkshop2020/doc/iSEE-lab.html>.
  This is a [known bug](https://github.com/rocker-org/rocker-versioned/issues/178).
